Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-05-12 paper2_JNLS/Referee Reports/Ref1Response/Ref1.tex
NM

\begin{itemize}
\item The referee is correct that equilibrium statistical mechanics and the canonical ensemble is used here, not because it is rigorously justified, but as an effective theory that explains the data.
It is true that the 1D KdV equation is an integrable system whose trajectories are constrained by an infinite number of conserved quantities. However, the {\em truncated} system does not possess these constraints (and pointed out in the original text).
%\begin{quotation}
%\end{quotation}
\item a
\end{itemize}

\noindent
\comment{}

>>>>

\begin{itemize}
\item First, thank you for these insightful comments. The referee is correct to point out that a sufficient amount of nonlinear interaction is  required for relaxation to the Gibbs measure, and we agree that this condition not being met is the most likely the explanation for formula (53) not matching the smallest-amplitude data in Fig. 8(c). We have inserted these points in the updated manuscript. In particular, see the passage in Section 3.5 (page 11):
\begin{quotation}
We also point out that a sufficient amount of nonlinear mixing is required for relaxation to the above Gibbs measure. In the linearized system, for example, modes propagate without interacting and hence the initial measure induced by the wave generator remains unchanged.
\end{quotation}
Also, see the passage describing Fig. 8(c) in Section 4.4 (page 22)
\begin{quotation}
The apparently less predictable behavior at small amplitudes can be attributed to the fact that, in order for the system to relax to the Gibbs measure, modes must interact through nonlinearity. For the smallest amplitude experiments, the amount of nonlinearity is apparently too small for  modes to mix sufficiently.
\end{quotation}
\item Have we included new references on integrable turbulence???
%\item The referee is correct that equilibrium statistical mechanics and the canonical ensemble is used here, not because it is rigorously justified, but as an effective theory that explains the data. It is true that the 1D KdV equation is an integrable system whose trajectories are constrained by an infinite number of conserved quantities. However, the {\em truncated} system does not possess these constraints (and pointed out in the original text).
%\begin{quotation}
%\end{quotation}
\end{itemize}

\noindent
\comment{
2. The authors may find it useful to compare their equation (53) to
 ``On the origin of heavy-tail statistics in equations of the Nonlinear Schrodinger type'', Onorato et al., Phys. Lett. A, 380, 89 (2016), 
 %where an analogous relationship is derived for NLS. It should be possible to relate the skewness to spectral variations, which may lead to further interesting investigations.
}

### 2020-05-12 paper2_JNLS/paper.tex
NM

The momentum and energy defined in \eqref{MomEn} remain invariants of TKdV, with the same normalized values $\Mo[\uL] = 0$ and $\En[\uL] = 1$. Note that Parseval's identity implies
\begin{equation}
\En[\uL] = 2 \pi \sum_{k=1}^{\Lambda} \abs{\uhat_k}^2 = 1
\end{equation}
% The above agrees with the first line on top of p. 4 in Majda and Qi J Stat Phys 2019.
Thus, the dynamics of interest are confined to the unit hypersphere, $\En = 1$ in $\CC^{\Lambda}$.
In summary, the TKdV system possesses three important invariants: momentum, energy, and Hamiltonian. The untruncated KdV equation possesses an infinite sequence of additional invariants \cite{lax1975periodic, whitham2011linear}, but their truncated counterparts are not generally invariants of TKdV.

>>>>

The momentum and energy defined in \eqref{MomEn} remain invariants of TKdV, with the same normalized values $\Mo[\uL] = 0$ and $\En[\uL] = 1$. Note that Parseval's identity implies
\begin{equation}
\En[\uL] = 2 \pi \sum_{k=1}^{\Lambda} \abs{\uhat_k}^2 = 1
\end{equation}
% The above agrees with the first line on top of p. 4 in Majda and Qi J Stat Phys 2019.
Thus, the dynamics of interest are confined to the unit hypersphere, $\En = 1$ in $\CC^{\Lambda}$.
In summary, the TKdV system possesses three important invariants: momentum, energy, and Hamiltonian.

\new{We comment on some important differences between the KdV and TKdV systems. The KdV system possesses in infinite sequence of additional invariants, associated with the fact that it is a completely integrable system. However, the analogues of these quantities are {\em not} generally invariants of the truncated system; no invariants beyond the three mentioned above are known to exist for TKdV. Hence, while KdV is a completely integrable system whose long-time dynamics are governed by soliton interactions, this same behavior should not be expected for TKdV. In particular, the long-time behavior is not simply governed by soliton motion and instead is chaotic and observed to be weakly ergodic \cite{bajars2013weakly}. In this way, the theory developed herein differs from, and could likely by complementary to, recent advances in the field of integrable turbulence \cite{zakharov2009turbulence, randoux2014intermittency, costa2014soliton, randoux2016nonlinear}, in which integrability is exploited in order to uncover statistical characteristics of the system of interest. 
}
\new{
We remind the reader that KdV is asymptotically valid for large spatial scales and hence truncating the small scales (or alternatively modeling them through closure) does not alter the order of approximation made. In this sense, KdV and TKdV should be viewed as on equal footing as far as physical realism.
Where differences exist in long-time dynamics, it is unclear which model, if either, more closely resembles reality.}
